Rising from the Ashes: A Metallicity-Dependent Star Formation Gap Splits the Milky Way's $\alpha$-Sequences

### 2025-02-14 paper/ms.tex
Add orcid
Add LLM/software citations

\author{Angus Beane}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}

@@

@@

>>>>

\author[0000-0002-8658-1453]{Angus Beane}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}

@@

We acknowledge the use of OpenAI’s ChatGPT and Anthropic's Claude for assistance in editing this manuscript for clarity and conciseness and in generating small analysis scripts and code snippets.

@@

\software{ {\sc astropy} \citep{astropy:2013,astropy:2018,astropy:2022}, {\sc h5py} \url{http://www.h5py.org/}, {\sc inspector\_gadget} \url{https://bitbucket.org/abauer/inspector_gadget/}, {\sc joblib} \url{https://joblib.readthedocs.io/en/latest/}, {\sc matplotlib} \citep{Hunter:2007}, {\sc numba} \citep{lam2015numba}, {\sc numpy} \citep{harris2020array}, {\sc scikit-learn} \citep{scikit-learn}, {\sc scipy} \citep{2020SciPy-NMeth}, {\sc tqdm} \url{https://tqdm.github.io/}, {\sc vortrace} \url{https://github.com/gusbeane/vortrace}}
